Inferring the effective start dates of non-pharmaceutical interventions during \covid outbreaks

### 2020-07-08 ms/ms.tex
update PPC plots; add table titles for RMSE and WAIC

%%%% Fig - NPI dates %%%
\begin{figure}[h]
    \centering
	\includegraphics[width=0.5\textwidth]{../figures/Fig-NPI_dates.pdf}
    \caption{
    \textbf{Official start of non-pharmaceutical interventions.}
	See \autoref{table:NPI_dates} for more details. Wuhan, China is not shown.
    } 
    \label{fig:NPI_dates}
\end{figure}

% Table - WAIC %%% TODO regenerate table
% generated with /python Table-WAIC.py 2020-05-26-Apr11/
\begin{table}[h]
\centering
\pgfplotstabletypeset[
    col sep=comma,
    string type,
    every head row/.style={before row=\hline,after row=\hline},
    every last row/.style={after row=\hline},
    ]{../figures/Table-WAIC.csv}
\caption{
\textbf{WAIC values for the different models.}
	WAIC (widely applicable information criterion; \autoref{eq:WAIC})~\citep{gelman2013bayesian} values for models  with: no $\tau$ at all, \emph{No}; $\tau$ fixed at the official last NPI date $\tau^*$, \emph{Fixed}; and free parameter $\tau$, \emph{Free}. WAIC values are scaled as a deviance measure: lower values imply higher predictive accuracy and a difference of 2 is a popular significance level for model comparison~\citep{Kass1995}. Bold values emphasize cases in which the \emph{Free} model has the lowest WAIC.
}
\label{table:WAIC}
\end{table}

% Table - RMSE 
% generated with /python Table-RMSE.py 2020-05-26-Apr11/
\begin{table}[h]
\centering
\pgfplotstabletypeset[
    col sep=comma,
    string type,
    every head row/.style={before row=\hline,after row=\hline},
    every last row/.style={after row=\hline},
    ]{../figures/Table-RMSE.csv}
\caption{
\textbf{Posterior RMSE of out-of-sample predictions with the different models.}
	Expected posterior predictive RMSE (root mean squared error) for models  with: no $\tau$ at all, \emph{No}; $\tau$ fixed at the official last NPI date $\tau^*$, \emph{Fixed}; and free parameter $\tau$, \emph{Free}.
	In all cases, the model with free parameter $\tau$ has the lowest RMSE.
	Models were fitted to case data up to Apr~11, 2020, and then used to generate 1,000 predictions from Apr~12 to Apr~24 by sampling model parameters from the posterior distribution.
	These predictions were then compared to the real data using RMSE, and the mean RMSE value is shown in the table for each country and model.
}
\label{table:RMSE}
\end{table}

@@

%%% Fig PPC %%% TODO UPDATE

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Austria_ppc.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Austria_ppc.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Belgium_ppc.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Belgium_ppc.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Denmark_ppc.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Denmark_ppc.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/France_ppc.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/France_ppc.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Germany_ppc.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Germany_ppc.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Italy_ppc.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Italy_ppc.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Norway_ppc.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Norway_ppc.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Spain_ppc.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Spain_ppc.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Sweden_ppc.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Sweden_ppc.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Switzerland_ppc.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Switzerland_ppc.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/United_Kingdom_ppc.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/United_Kingdom_ppc.pdf}

@@

%    %%%  
%	\subcaption{Wuhan, China}    
%    \begin{subfigure}{0.45\textwidth}
%        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Wuhan_ppc.pdf}
%    \end{subfigure}
%    ~
%    \begin{subfigure}{0.45\textwidth}
%        \includegraphics[width=\textwidth]{../figures/ppc/free/Wuhan_ppc.pdf}
%    \end{subfigure}

@@

    \textbf{Figure S4. Posterior prediction plots.}
    Markers represent data ($\vec{X}$): circles for data up to Apr~11, 2020, and stars after Apr~12; Apr~11 is represented using a vertical dashed line. Black line represents a smoothing of the data points using a Savitzky-Golay filter. Coloured lines represent posterior predictions from a model with fixed $\tau$ in red, and free $\tau$ in blue. The models were fitted with data up to Apr~11. The predictions are generated by drawing 1,000 parameters sets from the posterior distribution, and then generating a daily case count using the SEIR model in \autoref{eq:model}. Note the differences in the y-axis scale.

>>>>

%%%% Fig - NPI dates %%%
% generated with /python Fig_NPI_dates.py/
\begin{figure}[h]
    \centering
	\includegraphics[width=0.5\textwidth]{../figures/Fig-NPI_dates.pdf}
    \caption{
    \textbf{Official start of non-pharmaceutical interventions.}
	See \autoref{table:NPI_dates} for more details. Wuhan, China is not shown.
    } 
    \label{fig:NPI_dates}
\end{figure}

% Table - WAIC 
% generated with /python Table-WAIC.py 2020-05-26-Apr11/
\begin{table}[h]
\centering
\caption*{\textbf{WAIC}}
\pgfplotstabletypeset[
    col sep=comma,
    string type,
    every head row/.style={before row=\hline,after row=\hline},
    every last row/.style={after row=\hline},
    ]{../figures/Table-WAIC.csv}
\caption{
\textbf{WAIC values for the different models.}
	WAIC (widely applicable information criterion; \autoref{eq:WAIC})~\citep{gelman2013bayesian} values for models  with: no $\tau$ at all, \emph{No}; $\tau$ fixed at the official last NPI date $\tau^*$, \emph{Fixed}; and free parameter $\tau$, \emph{Free}. WAIC values are scaled as a deviance measure: lower values imply higher predictive accuracy and a difference of 2 is a popular significance level for model comparison~\citep{Kass1995}. Bold values emphasize cases in which the \emph{Free} model has the lowest WAIC.
}
\label{table:WAIC}
\end{table}

% Table - RMSE 
% generated with /python Table-RMSE.py 2020-05-26-Apr11/
\begin{table}[h]
\centering
\caption*{\textbf{RMSE}}
\pgfplotstabletypeset[
    col sep=comma,
    string type,
    every head row/.style={before row=\hline,after row=\hline},
    every last row/.style={after row=\hline},
    ]{../figures/Table-RMSE.csv}
\caption{
\textbf{Posterior RMSE of out-of-sample predictions with the different models.}
	Expected posterior predictive RMSE (root mean squared error) for models  with: no $\tau$ at all, \emph{No}; $\tau$ fixed at the official last NPI date $\tau^*$, \emph{Fixed}; and free parameter $\tau$, \emph{Free}.
	In all cases, the model with free parameter $\tau$ has the lowest RMSE.
	Models were fitted to case data up to Apr~11, 2020, and then used to generate 1,000 predictions from Apr~12 to Apr~24 by sampling model parameters from the posterior distribution.
	These predictions were then compared to the real data using RMSE, and the mean RMSE value is shown in the table for each country and model. 
	Bold values emphasize cases in which the \emph{Free} model has the lowest RMSE.
}
\label{table:RMSE}
\end{table}

@@

%%% Fig PPC

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Austria_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Austria_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Belgium_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Belgium_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Denmark_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Denmark_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/France_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/France_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Germany_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Germany_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Italy_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Italy_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Norway_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Norway_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Spain_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Spain_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Sweden_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Sweden_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/Switzerland_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/Switzerland_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/fixed/United_Kingdom_ppc_long.pdf}

@@

        \includegraphics[width=\textwidth]{../figures/ppc/free/United_Kingdom_ppc_long.pdf}

@@

@@

    \textbf{Figure S4. Posterior prediction plots for 11 European countries.}
    Circles and stars represent daily case data up to and after Apr~11, 2020, respectively, and the vertical dashed line represents Apr~11.
    Black lines represents a smoothing of the data points using a Savitzky-Golay filter. 
    Colored lines represent posterior predictions from a model with fixed $\tau$ -- blue -- and free $\tau$ -- green. Models were fitted with data up to Apr~11. The predictions are generated by drawing 1,000 parameters sets from the posterior distribution, and then generating a daily case count using the SEIR model in \autoref{eq:model}. Note the differences in the y-axis scale.
    Posterior predictions with the free $\tau$ model are good for all countries except Denmark and Sweden, but poor for the fixed $\tau$ model.
    The predictions of the model without $\tau$ (not shown) are even worse.
